---
title: "Video consumption behavior analysis"
author: "Haokai"
date: "2023-04-27"
output:
  word_document: default
  pdf_document: default
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)

library(dplyr)
library(readr)
library(ggplot2)

vcb <- read_csv(
'124-code-Survey on online video consumption behaviour.csv',
col_types = cols(
  col_factor(),
  col_factor(
    levels = c(
      '0-3 hours',
      '3-6 hours',
      '6-9 hours',
      '9 hours or more'
    ),
    ordered = TRUE
  ),
  col_number(),
  col_number()
))

```

# Visualise categorical variables
## Gender
```{r}
vcb %>%
  ggplot(aes(x = gender)) +
  geom_bar() +
  ggtitle('Gender of respondents')
```

## video consumption hours
```{r}
vcb %>%
  ggplot(aes(x = hours)) +
  geom_bar (binwidth = 5) +   
  ggtitle('video consumption hours of respondents')
```


# Visualise numeric variables
## identity sense
```{r}
vcb %>%
  ggplot(aes(x = identity_sense)) +
  geom_histogram(binwidth = 1) +
  ggtitle('level of identity sense')
```

## feedback_tendency
```{r}
vcb %>%
  ggplot(aes(x = feedback_tendency)) +
  geom_histogram(binwidth = 1) +
  ggtitle('feedback_tendency')
```

Which of the following statements match your video consumption behavior?(multiple choices)

*If needed, I would show my opinion by click “like”
*If needed, I would show my opinion 
*If needed, I would follow the broadcaster(uploader)
*If needed, I would reduce the number of similar videos by clicking on "not interested"
*If needed, I would send bullet comment to show my opinion

# Distribution of numeric variables
## identity_sense
```{r}
vcb %>%
  summarise(n = n(), Mdn = median(identity_sense), M = mean(identity_sense), SD = sd(identity_sense))
```

## feedback_tendency
```{r}
vcb %>%
  summarise(n = n(), Mdn = median(feedback_tendency), M = mean(feedback_tendency), SD = sd(feedback_tendency))
```



# Analysis
## feedback tendency by gender
```{r}
vcb %>%
  group_by(gender) %>%
  summarise(n = n(), Mdn = median(feedback_tendency), M = mean(feedback_tendency), SD = sd(feedback_tendency))
```

```{r}
vcb %>%
  filter(
    gender %in% c(
      'Male', 'Female')
  ) %>%
  t.test(
  formula = feedback_tendency ~ gender,
  var.equal = FALSE,   #方差不相等代表了这里用的是Welch's t test而不是student's t test
  data = .
  )
    
```


## video consumption hours by identity sense
```{r}
vcb %>%
  ggplot(aes(x = identity_sense, y = hours)) +
  geom_boxplot()
```

```{r}
vcb %>%
  cor.test(
    formula = ~ identity_sense + as.numeric(hours),
    method = 'spearman',
    exact = FALSE,
    data = .
  )
```

## feedback tendency by identity sense

```{r}
vcb %>%
  ggplot(aes(x = identity_sense, y = feedback_tendency)) +
  geom_jitter()
```

```{r}
vcb %>%
  cor.test(
    formula = ~ identity_sense + feedback_tendency,
    method = 'spearman',
    exact = FALSE,
    data = .
  )
```



